MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-09-17 MAESTROeX_I/appendix.tex
updated figs 4, 5, 8, 9 to have larger fonts

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\begin{tabular}{l c}
\multirow{4}{3.25in}[30mm]{ \includegraphics[width=3.0in]{./figs/wdconvect_256_splitU} } & \multicolumn{1}{c}{\includegraphics[width=2.35in]{./figs/magvel_full_XY}} \\
& \multicolumn{1}{c}{\begin{footnotesize} (a) Velocity magnitude, solved using full $\mathbf{U}$ \end{footnotesize}} \\[1.em]
& \multicolumn{1}{c}{\includegraphics[width=2.75in]{./figs/magvel_lineout_X}} \\ 
& \multicolumn{1}{c}{\begin{footnotesize} (b) Comparison along white line \end{footnotesize}} \\
\end{tabular}
\caption{\label{fig:wdconvect_splitU} When solving for the full velocity $\mathbf{U}$ in the nodal projection step instead of the split velocity 
  formulation, we illustrate
  (left) the peak temperature, $T_{\text{peak}}$ in a white dwarf at resolution of $256^3$ during the early evolution of the star and
  (right) the magnitude of velocity at early time. We observe much larger velocities outside the density cutoff region, $\rho < 10^5 \text{ g cm}^{-3}$, 
  that are not seen when we split the velocity dynamics.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\begin{tabular}{l c}
\multirow{4}{3.25in}[30mm]{ \includegraphics[width=3.0in]{./figs/wdconvect_256_splitU} } & \multicolumn{1}{c}{\includegraphics[width=2.35in]{./figs/magvel_full_XY}} \\
& \multicolumn{1}{c}{\begin{footnotesize} (a) Velocity magnitude, solved using full $\mathbf{U}$ \end{footnotesize}} \\[1.em]
& \multicolumn{1}{c}{\includegraphics[width=2.5in]{./figs/magvel_lineout_X}} \\ 
& \multicolumn{1}{c}{\begin{footnotesize} (b) Comparison along white line \end{footnotesize}} \\
\end{tabular}
\caption{\label{fig:wdconvect_splitU} When solving for the full velocity $\mathbf{U}$ in the nodal projection step instead of the split velocity 
  formulation, we illustrate
  (left) the peak temperature, $T_{\text{peak}}$ in a white dwarf at resolution of $256^3$ during the early evolution of the star and
  (right) the magnitude of velocity at early time. We observe much larger velocities outside the density cutoff region, $\rho < 10^5 \text{ g cm}^{-3}$, 
  that are not seen when we split the velocity dynamics.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
